---
title: "Data Science HW1"
format: html
editor: visual
---

## Question 1: What do you think being a data scientist is about?

I believe a data scientist is an individual that can effectively sort, manage, and manipulate data. I believe this to be especially true of larger and more complex datasets.Thus, data scientists are very applied.

## Question 2: What differences/similarities do you see between data scientists and statisticians?

I think a difference between the two is that data scientists may not have the theoretical or conceptual underpinnings that a statistician does. A similarity is that both understand how to manage and analyze data.

## Question 3: How do you view yourself in relation to these two areas?

I am an ecologist at App State so all of my projects generate data. I would not consider myself a statistician but because I do work with data, I would like to become a data scientist. I hope to improve my applied statistics skills and get more organized with the data that I collect for analysis.

## Running Code

```{r}
y <- density(iris$Petal.Width)
```

the above code has stored the petal width data in a file called "y"

```{r}
class(iris)
```

the above code has identified the class of the iris dataset in R.

```{r}
typeof(iris)
```

the above code has identified the type of data in the iris dataset in R.

```{r}
str(iris)
```

the above code has identified the structure of the iris dataset in R.

```{r, echo=FALSE}
plot(y)

```

the above code has plotted the "y" file that was generated in the 1st line of code.
